\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-05 popl-2019-journal-v/paper.tex
[POPLjv] Various typesetting
Related work on linear capabilities.

\section{Related Work}
In this section, we discuss related work on securely enforcing control flow correctness and/or local state encapsulation.
We do not repeat the work we discussed in Section~\ref{sec:introduction}.

@@

\dominique{TODO Relate to Thomas Van Strydonck's ICFP19 paper which uses linear capabilities (at a higher level) to enforce separation logic in a fully abstract way.}

>>>>

\section{Related Work}
In this section, we discuss related work on securely enforcing control flow correctness and/or local state encapsulation or the linear capabilities we use to do it.
We do not repeat the work we discussed in Section~\ref{sec:introduction}.

@@

In addition to the already-mentioned work on linear capabilities, \citet{van_strydonck_linear_2019} have recently used them in a secure (fully abstract) compiler for a C-like language with separation logic contracts.
A form of linear capabilities was also used in the SAFE machine developed within the CRASH/SAFE project \citep{DBLP:conf/sp/AmorimDGHPST15,DBLP:journals/jcs/AmorimCDDHPPPT16}.
